### 2014-11-02 thesis/method/selection.tex
Fix broken table and figure labels in latex

\subsection{Correlation-based Feature Selection (CFS)}
Correlation-based feature selection (CFS) is a method developed by Hall
\cite{Hall2000} which looks for a subset of features that have high correlation
with the class but low intercorrelation among the features. In this case,
correlation between two features is measured using what is called the
\textit{symmetric uncertainty}:
\begin{equation*}
U(A,B) = 2\dfrac{H(A)+H(B)-H(A,B)}{H(A)+H(B)}
\end{equation*}
where $A$ and $B$ are two nominal attributes and $H$ is the entropy function
denoted by Equation \ref{eqn:entropy} in Chapter \ref{chap:classification}.
The entropies are calculated from the probabilities of each feature value, and
$H(A,B)$, the joint entropy of $A$ and $B$, is calculated from the
probabilities of each combination of values of $A$ and $B$. Note that $U(A,B)$
is always between 0 and 1.

@@

\subsection{Pearson Correlation Coefficient (PCC)}
The Pearson correlation coefficient measures the degree of linear correlation
between two variables. It is always in the range $[-1,1]$, where -1 is total
negative correlation, 0 is no (linear) correlation, and 1 is total positive
correlation. We compute the Pearson correlation between each feature and the
class using:
\begin{equation*}
r_i = \dfrac{\sum_{i=1}^m (x_i-\bar{x})(c-\bar{c})}{\sqrt{(\sum_{i=1}^m x_i-\bar{x})(\sum_{i=1}^m c-\bar{c})}}
\end{equation*}
where $m$ is the number of training examples, $x_i$ is the value of feature
$i$, and $\bar{x}$ and $\bar{c}$ are the arithmetic averages of the feature
values and the class values respectively. (Recall that we also used this
in Chapter \ref{chap:classification} to rank features for use in Ranked
Distance nearest neighbours.)

@@

\subsection{Information Gain (IG)}
Recall from our discussion of decision trees in in Section \ref{sec:c45} that
the information gain (IG) is used to decide which attribute to split on at each
step of the tree. We can also measure the IG of each feature as follows.
If we have a class $C$ and a feature $F$, the entropy of the
class before and after observing the feature is:
\begin{equation*}
\begin{aligned}
& \mathrm{entropy}(C) = - \sum_{c \in C} p(c) \mathrm{log}_2 p(c) \\
& \mathrm{entropy}(C|F) = - \sum_{f \in F} p(f) \sum_{c \in C} p(c|f) \mathrm{log}_2 p(c|f)
\end{aligned}
\end{equation*}
The decrease in entropy reflects the gain in information provided by the
feature and is given by:
\begin{equation*}
IG(C|F) = \mathrm{entropy}(C) - \mathrm{entropy}(C|F)
\end{equation*}

@@

\subsection{Wrapper-based Feature Selection}
The feature selection methods described above (CFS, Pearson correlataion and
1R) have been described as \textit{filter} approaches to attribute selection.
Kohavi and John proposed another approach, the \textit{wrapper} approach:
instead of performing feature selection independently of the learning
algorithm using some measure of ``relevance'',
the learning algorithm itself is used to evaluate the goodness of
subsets of features \cite{Kohavi1997}. The difference between the filter
and wrapper approaches is depicted in Figure \ref{fig:wrapper}.

\begin{figure}[h]
\label{fig:wrapper}
\caption{}
\centering
%\includegraphics[scale=0.95]{images/a2-nn}
\end{figure}

>>>>

\subsection{Correlation-based Feature Selection}
Correlation-based feature selection (CFS) is a method developed by Hall
\cite{Hall2000} which looks for a subset of features that have high correlation
with the class but low intercorrelation among the features. In this case,
correlation between two features is measured using what is called the
\textit{symmetric uncertainty}:
\begin{equation*}
U(A,B) = 2\dfrac{H(A)+H(B)-H(A,B)}{H(A)+H(B)}
\end{equation*}
where $A$ and $B$ are two nominal attributes and $H$ is the entropy function
denoted by Equation \ref{eqn:entropy} in Chapter \ref{chap:classification}.
The entropies are calculated from the probabilities of each feature value, and
$H(A,B)$, the joint entropy of $A$ and $B$, is calculated from the
probabilities of each combination of values of $A$ and $B$. Note that $U(A,B)$
is always between 0 and 1.

@@

\subsection{Pearson Correlation Coefficient}
The Pearson correlation coefficient measures the degree of linear correlation
between two variables. It is always in the range $[-1,1]$, where -1 is total
negative correlation, 0 is no (linear) correlation, and 1 is total positive
correlation. We compute the Pearson correlation between each feature and the
class using:
\begin{equation*}
r_i = \dfrac{\sum_{i=1}^m (x_i-\bar{x})(c-\bar{c})}{\sqrt{(\sum_{i=1}^m x_i-\bar{x})(\sum_{i=1}^m c-\bar{c})}}
\end{equation*}
where $m$ is the number of training examples, $x_i$ is the value of feature
$i$, and $\bar{x}$ and $\bar{c}$ are the arithmetic averages of the feature
values and the class values respectively. (Recall that we also used this
in Chapter \ref{chap:classification} to rank features for use in Ranked
Distance nearest neighbours.)

@@

\subsection{Information Gain}
Recall from our discussion of decision trees in in Section \ref{sec:c45} that
the information gain (IG) is used to decide which attribute to split on at each
step of the tree. We can also measure the IG of each feature as follows.
If we have a class $C$ and a feature $F$, the entropy of the
class before and after observing the feature is:
\begin{equation*}
\begin{aligned}
& \mathrm{entropy}(C) = - \sum_{c \in C} p(c) \mathrm{log}_2 p(c) \\
& \mathrm{entropy}(C|F) = - \sum_{f \in F} p(f) \sum_{c \in C} p(c|f) \mathrm{log}_2 p(c|f)
\end{aligned}
\end{equation*}
The decrease in entropy reflects the gain in information provided by the
feature and is given by:
\begin{equation*}
IG(C|F) = \mathrm{entropy}(C) - \mathrm{entropy}(C|F)
\end{equation*}

@@

\subsection{Wrapper-based Feature Selection}
The feature selection methods described above (CFS, Pearson correlation and
1R) have been described as \textit{filter} approaches to attribute selection.
Kohavi and John proposed another approach, the \textit{wrapper} approach:
instead of performing feature selection independently of the learning
algorithm using some measure of ``relevance'',
the learning algorithm itself is used to evaluate the goodness of
subsets of features \cite{Kohavi1997}. The difference between the filter
and wrapper approaches is depicted in Figure \ref{fig:wrapper}.

\begin{figure}[h]
\caption{Filter and wrapper approaches to feature selection. Note the role of
the learning algorithm in the wrapper method.}
\label{fig:wrapper}
\centering
%\includegraphics[scale=0.95]{images/a2-nn}
\end{figure}
